### 2010-12-01 report/report.tex
Edited report more...

\section{Evaluation status}
% A list of the major steps in your planned evaluation of the system
% and the status of each. For some projects it may be easier to merge
% this list with the component/module status list above of your
% system. Include also who in the team is responsible for completing
% this module.

\begin{itemize}
\item After running our program and finding a good gait, we will then
evaluate our system by the distance walked in a certain amount
of time. This evaluation metric depend on the result of
running our program for many iterations. We have done 50 runs of 
3 different inital parameter vectors for random hill climbing, 
gaussian random hill climbing, and policy gradient descent.
The evaluation for our particular project is an ongoing
process, but we anticipate a final evaluation taking place
early-to-mid November. The evaluation process will be completed by
Jason, Sarah, and Diana.

@@

\section{Project schedule timeline}
% Tell us if you are meeting your project timeline or you are
% exceeding it or falling behind. If you are falling behind, explain
% how you will catch up or adjust the goals.

We are meeting our project timeline. We have developed two new algorithms,
gaussian hill climbing and policy gradient descent and tested all three of
our major algorithms on the robot. We have also quantified our current results. 
In the next month we hope to develop one more learning strategy, machine
learning of an objective function.

\section{Schedule}

Below is a rough schedule of fixed external deadlines and anticipated
team milestones.

\definecolor{doneColor}{rgb}{0.0,0.7,0.0}
\newcommand{\done}[1]{{\color{doneColor}\sout{#1}}}
%\newcommand{\done}[1]{#1}

\begin{center}
\begin{tabular}{|l||p{2.5in}|p{1.5in}|}
\hline
                        & {\bf Milestones} & {\bf Deadlines}
\\ \hline

Week 1 (9/13-9/19)    & \done{Read papers, get lab access, talk to relevant other researchers} & 9/17 Final proposals due
\\ \hline

Week 2 (9/20-9/26)    & \done{Continue reading, get robot to move} &
\\ \hline

Week 3 (9/27-10/03)   & \done{Implement parametrized gait and determine proposed coding schedule for more advanced algorithms in time for Code Review \#1.} &
\\ \hline

Week 4 (10/04-10/10)  & \done{Begin main algorithm dev/testing effort} & 10/5 Code Review \#1
\\ \hline

Week 5 (10/11-10/17)  & \done{Algorithm dev/testing} &
\\ \hline

Week 6 (10/18-10/24)  & \done{Algorithm dev/testing} &
\\ \hline

Week 7 (10/25-10/31)  & \done{Algorithm dev/testing, quantify/solidify current results for Code Review \#2} &
\\ \hline

Week 8 (11/1-11/7)    & \done{Finish collecting results, begin writing} & 11/2 Code Review \#2
\\ \hline

Week 9 (11/8-11/14)   & Algorithm dev/testing &
\\ \hline

Week 10 (11/15-11/21) & Finish collecting results, writing, get final demo ready &
\\ \hline

Week 11 (11/22-11/28) & Finish collecting results, writing, get final demo ready  &
\\ \hline

Week 12 (11/29-11/30) & Final demo  & 11/30 Final presentation
\\ \hline
\end{tabular}
\end{center}

\section{Activity log (Optional)}

% an informal log your efforts. If you’ve been keeping notes on your
% progress, feel free to turn these in as well. These might include:
% (1) notes on what aspect of the project you worked on and when, (2)
% what was accomplished in each “session”, (3) design questions, (4)
% implementation questions, (5) descriptions of experiments and
% results, (6) problems that arose, (7) anything else that you think
% is relevant to the project.

\begin{itemize}
\item \emph{9/13-9/19:} Set up. Set up trac, worked on pre-proposal
  and presentation, got lab access, met with Jim Torresen, contacted
  Juan Cristobal Zagal, read papers, got the robot to walk using
  previously coded program. Questions -- How do we move the robot? How
  do we command the motors?
\item \emph{9/20-9/26:} Moving the robot. Installed Linux on the
  robot, figured out how to command the motors, coded a program to
  make the robot stand up, coded a simple motion pattern. Questions --
  For initial program, what parameters and model should be used? How
  do we limit the search space? What algorithm should we start with?
  How will the robot get information about how far it moved?
\item \emph{9/27-10/3:} Initial program. Chose several parameters and
  created a simple parameterized sine model, implemented a random hill
  climbing algorithm to optimize the parameters, ran some trial
  iterations, began setting up the cameras for feedback. Questions --
  Did the initial program work? What parameters are important? Are
  additional parameters necessary? What algorithm should we implement
  for the final program?
\item \emph{10/4-10/10:} Plan for final implementation. Discussed
  possible algorithms to use and new parameters to add. Worked on
  report for code review. Discussed feedback from code review.  Questions -- Advantages for gradient
  descent? Should we start with a completely random parameter vector
  or should we start with one that results in motion and let the
  program optimize it? How does the camera system work?
\item \emph{10/11-10/17:} Discussed how we were going to proceed with the project and set up a more detailed schedule. Got the cameras working and calibrated them. Researched the 3 available streaming protocols. Questions -- Which streaming protocol would work best? Which improvements should we start with?
\item \emph{10/18-10/24:} Created a variation on the random hill climbing algorithm to choose the next neighbor based on a Gaussian distribution. Tried to work with two of the streaming protocols for the camera system, but were unsuccessful. Decided to use a Wii remote for positional information instead. Wrote the integration code for the Wii remote. Refactored our code to separate the different algorithms. Began planning the algorithm for a modified gradient descent.
Questions -- What values should we use in the gradient descent algorithm? How much should the each parameter be changed? How many neighbors should be sampled before choosing the next state? How can we compare the results of our different algorithms? How repeatable is the distance traveled for a given parameter vector?
\item \emph{10/25-11/2}: Created a modified gradient descent algorithm. Ran 150 trials of the three algorithms. Each algorithm started with a specific parameter vector and ran for 50 iterations. Created and ran a program to get a feel for the overall look of the search space. Ran some trials to see how reproducible the distance traveled was. Prepared for code review 2. Questions -- What does the search space look like? Are there a lot of spikes, or is it fairly smooth? Based on the results of the algorithms, what conclusions can we draw?
\end{itemize}

\section{Proposal Modifications}
% Let us know if you are deviating from your original proposal.

We are not deviating from our original proposal.

>>>>

\section{Experimental (or Theoretical) Evaluation}

\subsection{Methodology}
% What are the criteria you are using to evaluate your method? What
% specific hypotheses does your experiment test? Describe the 
% experimental methodology that you used. What are the dependent and 
% independent variables? For projects in machine learning, what is 
% the training/test data that was used, and why is it realistic or
% interesting? Exactly what performance data did you collect and how 
% are you presenting and analyzing it? Comparisons to competing methods 
% that address the same problem or to variations of your own algorithm 
% are particularly useful.
\begin{itemize}
\item Each algorithm was run on 3 different initial parameter vectors on the
physical robot. We stop each run after plateauing results (no improvement 
for half the policies seen so far). We evaluate each method based on the
amount of improvement seen from the initial parameter vectors, and on the
fastest speeds achieved during runs.
\end{itemize}

\subsection{Results}
% Present the quantitative results of your experiments. Graphical data
% presentation such as graphs and histograms are frequently better 
% than tables. Explain what are the basic differences revealed in the 
% data. If your method is stochastic or you analyze multiple datasets, 
% calculate mean and standard error for every quantitative
% performance result you show based on multiple runs.
\begin{itemize}
\item We have done runs of 
3 different inital parameter vectors for random hill climbing, 
gaussian random hill climbing, policy gradient descent, random,
simplex, and linear regression. We developed several
gaits that were about 4 times faster than the original hand-coded gait.

@@

\subsection{Discussion}
% Is your hypothesis supported? What conclusions do the results support
% about the strengths and weaknesses of your method compared to other 
% methods? How can the results be explained in terms of the underlying 
% properties of the algorithm and/or the data.

\section{Future work}
% What are the major shortcomings of your current method? For each 
% shortcoming, propose additions or enhancements that would help overcome it.
\begin{itemize}
\item Different motion representations
\item Evolutionary algorithms/HyperNEAT\cite{2}
\item Learning how to turn
\item Open sourcing code for others to extend
\end{itemize}

\section{Conclusion}
% Briefly summarize the important results and conclusions presented in 
% the paper. What are the most important points illustrated by your 
% work? How will your results improve future research and applications 
% in the area?
Because the fastest learned walk was not
significantly faster than the fastest randomly generated walk, we
conjecture that the motion representation for the robot is more
integral to forward speed than the learning algorithm.

\section{References}
% A numbered list of all books, articles, and web pages you used in your 
% work or that you cited in your report. Each item must be cited from 
% somewhere within the text. When citing a URL, include date visited. 
% When citing a commercial product, list the company.

\section{Acknowledgments}
% List any people not on the team who helped you with your project: Your
% TA, other people you consulted with or had useful discussions (say in 
% a word or two what they did), people who proofread your report, and 
% any external code you used (libraries etc).
